---
title: "Locus of X(131)-of-Orthic (Homothetic Poncelet)"
author: Dan S. Reznik
date: August 29, 2020
output:
  html_document:
    theme: sandstone
    highlight: tango
---

Visualization of loci of centers of ellipse-mounted triangles. 

Para el amigo Antonio Sánchez Chinchón `@aschinchon`

```{r,message=F}
library(tidyverse)
library(ggforce)
source("utils.R")
source("tri.R")
source("mount.R")
```

# Intro 

Visualization of loci of centers of ellipse-mounted triangles using R's ggplot.

## X(131)-of-orthic

Family: Poncelet 3-periodics within two homothetic ellipses.

```{r}
calc_and_draw(2.91,20.0,0.2,
              mount_homothetic,tri_orthic,tri_X131)
```

## X(138)-of-orthic

$V_1$ and $V_2$ mounted on ellipse vertices, and $P(t)$ slides over ellipse.

```{r}
calc_and_draw(2.6,20.0,0.1,
              mount_major,tri_orthic,tri_X138)
```

# More Info:

+ [github](https://github.com/dan-reznik/ellipse-mounted-triangles-ggplot-R)
+ [js app](https://bit.ly/3gzeCli)
+ [more info](https://dan-reznik.github.io/ellipse-mounted-triangles/)
+ [ETC]

*Chevere!*
